Two applications of logic programming to Coq

### 2021-03-05 papers/types2020/revisions/sec3.tex

Figure~\ref{fig:augmented} contains these proof rules and extends them
in the following ways so that it more appropriately fits into
the Coq proof system.
\begin{enumerate}
  \item Instead of having separate connectives for $\forall$ and
    $\supset$, we have the dependent product connective $(x:A)D$. 
  \item We account for \emph{computation} inside atoms by generalizing
    the \emph{init} rule to work modulo conversion.
  \item We have incorporated both \emph{proof certificates}~\cite{chihani17jar} (using the
    schematic variable $\XXi$) along with expert predicates
    (predicates with the $e$ subscript). We explain this in Section~\ref{ssec:cert}.
  \item The inference rules are  annotated by terms structures that
    can be given directly to the Coq kernel for checking.
  \item We have added various premises which are responsible for
    pulling information across  Coq's global environment.
\end{enumerate}
The proof system described in Figure~\ref{fig:augmented} (and
implemented in Figure~\ref{fig:kernel}) corresponds to a subset of the Calculus
of Inductive Constructions in which inductive definitions are
limited to % first-order
Horn clauses.
%
This  system is inspired by the calculus for proof search in
Pure Type Systems introduced in \cite{LengrandDM06}, based in turn on
ideas stemming from focusing (in particular, the LJT calculus of
Herbelin \cite{Herbelin94}). Similar to that calculus, we have a
term language that includes terms and lists of terms, and two distinct
typing judgments for the two categories.
% %
% In our case, the \lP goal formula \lsti{(check Xi (go B T))}
% corresponds to $\XXi\vdash B \colon T$ and the formula
% %
% \lsti{(check Xi (bc D B L))} corresponds to $\XXi\Downarrow L\colon
% D\vdash B$.
%
This style of  proof terms coincides with the idea behind the \emph{spine
  calculus}~\cite{Cervesato97tr}.  The main novelty of our proof
system here is that proof terms and proof certificates are used
simultaneously in all inference rules.

>>>>

Figure~\ref{fig:augmented} contains an annotated version of these
proof rules: the annotations help us connect to elements of the Coq
proof system.
\begin{enumerate}
  \item Instead of having separate connectives for $\forall$ and
    $\supset$, we have the dependent product connective $(x:A)D$. 
  \item We account for \emph{computation} inside atoms by generalizing
    the \emph{init} rule to allow for term-level conversion.
  \item We have incorporated both \emph{proof
  certificates}~\cite{chihani17jar} (using the schematic variable
    $\XXi$) along with expert predicates (predicates with the $e$
    subscript). We explain these in Section~\ref{ssec:cert}.
  \item The inference rules are  annotated by terms structures that
    can be given directly to the Coq kernel for checking.
  \item We have added various premises which are responsible for
    pulling information from Coq's global environment.
\end{enumerate}
The proof system described in Figure~\ref{fig:augmented} (and
implemented in Figure~\ref{fig:kernel}) corresponds to a subset of the Calculus
of Inductive Constructions in which inductive definitions are
limited to % first-order
Horn clauses.
%
This  system is inspired by the calculus for proof search in
Pure Type Systems introduced in \cite{LengrandDM06}, based in turn on
ideas stemming from focusing (in particular, the LJT calculus of
Herbelin \cite{Herbelin94}). Similar to that calculus, we have a
term language that includes terms and lists of terms, and two distinct
typing judgments for the two categories.
% %
% In our case, the \lP goal formula \lsti{(check Xi (go B T))}
% corresponds to $\XXi\vdash B \colon T$ and the formula
% %
% \lsti{(check Xi (bc D B L))} corresponds to $\XXi\Downarrow L\colon
% D\vdash B$.
%
This style of  proof terms coincides with the idea behind the \emph{spine
  calculus}~\cite{Cervesato97tr}.  The main novelty of our proof
system here is that proof terms and proof certificates are used
simultaneously in all inference rules.
